### 2018-02-08 usenix18/ex.tex
nits here and there

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.
\vspace{-0.1in}
\paragraph{\tool compiler.}
\tool compiler takes as input a source program and produces a C++
program as output. \figureref{ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in \figureref{ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.
\vspace{-0.2in}
\begin{figure}[h]
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\textbf{{\color{blue}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$

>>>>

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.
\vspace{-0.1in}
\paragraph{\tool compiler.}
\tool compiler takes as input a source program and produces a C++
program as output. \figureref{ex-aby} shows the output code for
the example in \figureref{ex-sml} -- this is also how a program written directly in
  ABY would look like. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.
%\vspace{-0.2in}

\begin{figure}[h]
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\textbf{{\color{blue}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$
